RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2013-12-17 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Move the TeX file over to Rnw and update the makefile to run Sweave so we can more quickly insert example usage sections in the document.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@560 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

TODO(ms): random citations to work in:

We make use of Object Tables \citep{RObjectTables} for lookup.
Many sources compare data serialization formats and show protocol
buffers very favorably to the alternatives, such
as \citep{Sumaray:2012:CDS:2184751.2184810}

>>>>

TODO(ms): Also work in reference to Split-Apply-Combine pattern for
data analysis \citep{wickham2011split}, since that is a great pattern
but it seems overly optimistic to expect all of those phases to always
be done in the same language.

@@

TODO(ms): random citations to work in:
q
We make use of Object Tables \citep{RObjectTables} for lookup.
Many sources compare data serialization formats and show protocol
buffers very favorably to the alternatives, such
as \citep{Sumaray:2012:CDS:2184751.2184810}
